---
name: Gaurav
surname: Dwivedi
position: "Technical Lead"
address: "Air Force Station, Viman Nagar, Pune, Maharastra"
phone: +91 8971856124
profilepic: gaurav.jpg
email: "gtgindia@gmail.com"
github: gtgindia
linkedin: gtgindia
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Working as a Technical Lead in TCS in Lifesciences Domain for a supply-chain project. Leading a team of data scientist involved in data ETL to forcasting demand to visualization. MBA in finance with total 3.5+ Years of experience in leading team including in finance & insurance industry."
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Work Experience

## __Tata Consultancy Services__                (Jul, 2021 - Till Date) _Technical Lead_ \linebreak


  __Project__ : Leading a team of 14 developer for European Pharmaceutical & Healthcare giant Bayer AG.
The project is focused on creating and maintaining a dashboard for the supply chain of a major drug.
Gives users a span shot of the current inventory level through various graphs and also helps them in
planning for future demand. We had various analytics tools built into the dashboard.  

 
With a proven capability to work independently and in teams, mentor co-workers, and communicate with
both technical and non-technical audiences, I consistently deliver value to clients.

\hfill
  __Project Scope__ : 
  
  + R language along with Shiny, dplyr, data.table , ggplot2
  + AWS EC2, RDS, ECS, lambda
  + Git Gitlab
  + Python for demand/supply calculation and forecasting 
  + Docker 
  
\hfill
  __Project Details__ : Project had three milestones. First to add UI improvements in the dashboard, this included adding graphs, filters etc. Second was to add 

## __ICICI Prudential Life Insurance__     (Sep, 2018 - Oct, 2019) _Manager_ \linebreak
  
  
## __Janalakshmi Financial Services__              (May, 2017 - Jun, 2018) _Assistant Manager_ 
  
\hfill\break
\hfill\break

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Science, Big Data Analytics", "2019-21", "Central University of Rajasthan", "Ajmer, Rajasthan    78.75%",
  "Master of Business Administration, Finance", "2014-16", "Symbiosis Institute of Management Studies, SIU", "Pune, Maharastra    70.73%",
  "Bachelor of Engineering, Computer Science Engineering", "2010-14", "Acharya Institute of Technology, VTU", "Bangalore, Karnataka    71.19%,",
  "HSC 12th CBSE", "2010", "Kendriya Vidyalaya", "Bidar, Karnataka    81.60%,",
  "SSC 10th CBSE", "2008", "Kendriya Vidyalaya", "Bidar, Karnataka    91.20%,"
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Certifications and Accomplishments

* AWS Certified Cloud Practitioner
* Won multiple awards in _Quiz Contests_ in school and Collage at various levels
* Worked in _Connecting NGO_ helping in suicide prevention
* Won On-The-Spot award in TCS
* Got multiple appreciations from client


